---
title: "EDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the data

```{r}
dat <- read_csv("../data/processed/mbr_all_final.csv")
dat <- as.data.frame(dat)
```

## Data Overiview

```{r}
# Convert some columns to factors
cols_factor = c("rim_status_closed", "type", "missing_payment")
dat[cols_factor] <- lapply(dat[cols_factor], as.factor) 
glimpse(dat)
```

```{r}
summary(dat)
```
1. rim_status_closed: whether the customer has churned (closed the bank membership), 1 indicates churn.
2. age: member age
3. type: membership type
4. moving_time: how many time a member has moved to a different zipcode
5. rim_duration: membership time
6. member_id: member id
7. rim_closed_dt: membership closed date
8. total_acct: total account a member has
9-17. CK-VISAS: total (type of account) a member has
18. mrm: member relationship score: 1= low - 4= high
19. trm: term (in months) tied to the account
20. cur_bal: current all accounts balance per member
21. orig_amt:  opening all accounts balance per member
22. orig_rate: average original rate of all accounts per member
23. acc_duration: average account duration of all accounts per member
24. online_duration: how long a member had and used the online banking
25. missing_payments: whether a member missed a payment (on loans)
26. avg_bal: average balance across all accounts per member
27. avg_rate: average rate across all accounts per member
28. total_amt: total aggregated transaction amount
29. total_ct: total count of transactions
30. avail_bal: total available balance to borrow
31. branch_rating: response to "Please rate the service you received at the XX branch today" on scale= 1 (poor) to 5 (excellent)
32. member_rating: response to "Please rate your new account opening experience" on scale= 1 (poor) to 5 (excellent)
33. contract_rating: response to "Please rate your new loan opening experience" scale= 1 (poor) to 5 (excellent)
34. mortgage_rating: response to "Please rate your home loan experience" scale= 1 (poor) to 5 (excellent)
35. email_rating: response to "Please rate your email experience" scale= 1 (poor) to 5 (excellent)

## Response variable
rim_status_closed = 0: non-churned customer
rim_status_closed = 1: churned customer

```{r}
ggplot(dat, aes(rim_status_closed, fill = rim_status_closed)) +
  geom_bar() +
  theme(legend.position = 'none')

table(dat$rim_status_closed)
round(prop.table(table(dat$rim_status_closed)),3)
```

Majority of the customers did not churn; only 12% churned.

## Feature variables
### Continuous Variable Distribution

```{r}
dat_graph <- dat %>%
  keep(is.numeric) %>%
  gather() 
  
```

```{r}
dat_graph %>% ggplot() +
  geom_histogram(mapping = aes(x=value,fill=key), color="black") +
  facet_wrap(~ key, scales = "free") +
  theme_minimal() +
  theme(legend.position = 'none')
```
### Correlation Matrix
```{r}
numericVarName <- names(which(sapply(dat, is.numeric)))
corr <- cor(dat[,numericVarName], use = 'pairwise.complete.obs')
ggcorrplot(corr)
```

#### Age distribution

```{r}
age_hist <- ggplot(dat, aes(x = age, fill = rim_status_closed)) +
  geom_histogram(binwidth = 5) +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0,100,by=10), labels = comma)

age_boxplot <- ggplot(dat, aes(x = rim_status_closed, y = age, fill = rim_status_closed)) +
  geom_boxplot() + 
  theme_minimal() +
  theme(legend.position = 'none')

age_hist | age_boxplot

```

#### Membership time distribution

```{r}
rim_duration_hist <- ggplot(dat, aes(x = rim_duration, fill = rim_status_closed)) +
  geom_histogram() +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0,20000,by=1000), labels = comma) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) 

rim_duration_boxplot <- ggplot(dat, aes(x = rim_status_closed, y = rim_duration, fill = rim_status_closed)) +
  geom_boxplot() + 
  theme_minimal() +
  theme(legend.position = 'none')

rim_duration_hist  
rim_duration_boxplot

```

### Categorical Variable Distribution

```{r}
dat %>%
  dplyr::select(-rim_status_closed) %>% 
  keep(is.factor) %>%
  gather() %>%
  group_by(key, value) %>% 
  summarize(n = n()) %>% 
  ggplot() +
  geom_bar(mapping=aes(x = value, y = n, fill=key), color="black", stat='identity') + 
  coord_flip() +
  facet_wrap(~ key, scales = "free") +
  theme_minimal() +
  theme(legend.position = 'none')
```

end